\texteparacol{\lettrine{P}{a}ter noster, qui es in cælis, san\-ctificétur nomen tuum: advéniat regnum tuum: fiat volúntas tua, sicut in cælo et in terra. Panem nostrum quotidiánum da nobis hódie: et dimítte nobis débita nostra, sicut et nos dimíttimus debitóribus nostris: et ne nos indúcas in tentatiónem: sed líbera nos a malo. Amen.

\lettrine{A}{v}e María, grátia plena; Dóminus tecum: benedí\-cta tu in muliéribus, et benedí\-ctus fru\-ctus ventris tui Jesus. Sancta María, Mater Dei, ora pro nobis peccatóribus, nunc et in hora mortis nostræ. Amen.

\lettrine{C}{r}edo in Deum, Patrem omnipoténtem, Creatórem cæli et terræ. Et in Jesum Christum, Fílium ejus únicum, Dóminum nostrum: qui concé\-ptus est de Spíritu Sancto, natus ex María Vírgine, passus sub Póntio Piláto, crucifíxus, mórtuus, et sepúltus: descéndit ad ínferos; tértia die resurréxit a mórtuis; ascéndit ad cælos; sedet ad déxteram Dei Patris omnipoténtis: inde ventúrus est judicáre vivos et mórtuos. Credo in Spíritum San\-ctum, sanctam Ecclésiam cathólicam, San\-ctórum communiónem, remissiónem peccatórum, carnis resurre\-ctiónem, vitam ætérnam. Amen.}{english}{\noindent Our Father, who art in heaven, Hallowed be thy name. thy kingdom come. thy will be done on earth as it is in heaven. Give us this day our daily bread. And forgive us our trespasses, as we forgive those who trespass against us. And lead us not into temptation: But deliver us from evil. Amen.

\noindent Hail Mary, full of grace, the Lord is with thee; blessed art thou amongst women, and blessed is the fruit of thy womb, Jesus. Holy Mary, Mother of God, pray for us sinners, now and at the hour of our death. Amen.

\noindent I believe in God, the Father almighty, Creator of heaven and earth. And in Jesus Christ, his only Son, our Lord; who was conceived by the Holy Ghost, born of the Virgin Mary, suffered under Pontius Pilate, was crucified, died and was buried: he descended into hell; the third day he arose again from the dead; he ascended into heaven; sitteth at the right hand of God the Father almighty: from thence he shall come to judge the living and the dead. I believe in the Holy Ghost, the holy catholic Church, the communion of Saints, the forgiveness of sins, the resurrection of the body, and life everlasting. Amen.}
